Dynamic Transition Analysis with TIMES

### 2019-01-08 doc/2019-01-poster/poster.tex
Update poster.tex

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
\end{block}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints.\hfill \break

@@

We have modeled \textbf{four scenarios:}

\begin{description}
        \item[\textbf{Scenario 1:}]
        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled (Fig. \ref{s1e} and \ref{s1c}.

        \item[\textbf{Scenario 2:}]
        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{except new ABWR reactors}, enabled (Fig. \ref{s2e} and \ref{s2c}).

        \item[\textbf{Scenario 3:}]
        I$^2$CNER technologies \textbf{enabled}.  Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled. (Fig.\ref{s3e} and \ref{s3c}).

        \item[\textbf{Scenario 4:}] 
 I$^2$CNER technologies \textbf{enabled}. Deployment of all conventional technologies, \textbf{excluding new ABWR reactors}, enabled (Fig.\ref{s4e} and \ref{s4c})

\end{description}

@@

%\vspace{11mm}

@@

>>>>

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\

Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}. \hfill \break

%\vspace{77mm}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints. \hfill \break

@@

We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break

\begin{tabular}{c c c c c}

\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
1                 & Fig. \ref{s1e}\&\ref{s1c}&        Yes                 &           No         &       Yes            \\ 
2                 & Fig. \ref{s2e}\&\ref{s2c}&        Yes                 &           No         &       No             \\ 
3                 & Fig. \ref{s3e}\&\ref{s3c}&        Yes                 &           Yes        &       Yes            \\ 
4                 & Fig. \ref{s4e}\&\ref{s4c}&        Yes                 &           Yes        &       No             \\
\end{tabular}

@@

\vspace{65 mm}

@@

    \item Making transitions more gradual.
